### 2021-04-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

The evaluated algorithms can be classified into two categories: symmetric
encryption and asymmetric encryption.

Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations.
\tool{} confirms that those leakage comes from table lookups. The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem. Those changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.

We also evaluate our tool on the RSA implementation. With the optimization
introduced in the previous sections, we need not apply domain knowledge to
simplify the analysis. Our tool identifies all leakage sites
reported by CacheD~\cite{203878} and find new leaks in less time.
We also find newer versions of RSA in OpenSSL have fewer leaks.

@@

The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. Under the circumstance, we think it is only a leakage.
We have confirmed that \tool{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \tool{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \tool{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours to process
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While those optimizations do not introduce false positives, they may miss some
vulnerabilities.
We notice that the number of instructions in those traces are different due to the different analysis starting
functions and building options during the evaluation.
Table~\ref{eval:cacheD} shows that
\tool{} is faster than CacheD. \tool{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\tool{} on AES from OpenSSL
0.9.7, \tool{} is over 100x faster than CacheD.
\begin{table*}[]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}

    \begin{tabular}{@{}c|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
      \hline
      \multicolumn{1}{l|}{} & \multicolumn{3}{c|}{CacheD} & \multicolumn{3}{c}{Abacus}                                             \\
      Name                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
      AES\tnote{1}          & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
      AES\tnote{2}          & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
      RSA\tnote{1}          & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
      RSA\tnote{2}          & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
      RSA\tnote{3}          & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
      RSA\tnote{4}          & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
      Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \tool: 12,489}                                 \\ \hline
    \end{tabular}

\end{table*}
DATA~\cite{217537} identifies
side-channel leakages by finding differences in execution traces of
the test program under \emph{various secret inputs}. According to
the original DATA paper, it uses 443 different traces to analyze the
side-channel vulnerabilities in symmetric cyphers and 450 different
traces to analyze the side-channel vulnerabilities in asymmetric
cyphers. On the other hand, \tool{} detects side-channel
vulnerabilities from one execution trace. \tool{} uses symbolic
analysis to extract formulas that model each side-channel
leakage. After that, we sample the formula with \emph{various
  secret inputs} to detect and quantify each leakage site. In
theory, DATA might have better code coverage than \tool{} because it
uses more execution traces,  but \tool{} has the following
advantages. a) \tool{} is faster than DATA. For example, it takes
116 minutes for DATA to detect vulnerabilities in the RSA implementation in OpenSSL 1.1.0f\@. \tool{} only spends 34 minutes, as shown in Table~\ref{table:over_result}. It takes 13 minutes and 20 minutes
for DATA to analyze the side-channel leakages in AES and DES,
respectively. On the other hand, \tool{} finishes its analysis in
less than ten seconds while finding all the leakages reported by
DATA. b) Because \tool{} does not run the test program again when we
have a new \emph{secret input}, \tool{} can test more input secrets
on those formulas within the same time to achieve better precision.
c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
The strength of Abacus is that it does not need such domain knowledge.
DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
\tool{} finds the vulnerability and reports the vulnerability is
severe (\textsf{int\_bn\_mod\_inverse} leaks more than 14.9 bits and
\textsf{BN\_div} leaks more than 17.2 bits), which helps identify
real sensitive leaks.  For each leakage site, \tool{} can provide
concrete examples to trigger the issue and give an estimation to
assess the severity level of the vulnerability.
\section{Discussion and Limitation}

In the section, we discuss the limitations, usages, and some future work.
%
\tool{} works on native x86 execution traces. The design, which is very
precise in terms of true leakages compared to other static source code
method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has
the common limitations of dynamic approaches. \tool{} may only cover part of the code.
% Each time we only get one single execution trace. Therefore,
We may
neglect some side-channel vulnerabilities not covered by the traces analyzed.
However, this is not a crucial problem for analyzing crypto libraries because crypto
libraries are designed to have the same code coverage for various inputs. Our
evaluation also confirms the above point. For symmetric encryption, during our
evaluation there is no secret-dependent control-flow transfers. RSA
implementations have several secret-dependent control-flow transfers.
%But after we manually check those leakages cites. We find
Most of them are  %used for
bound checks, which do not leak much information and have negligible effects
on the whole code coverage as well.

>>>>

The evaluated algorithms can be classified into two categories: symmetric
encryption and asymmetric encryption. Most of the side-channel leakages in symmetric implementations are from the lookup tables. The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem.

We also evaluate our tool on the RSA implementation. With the optimization
introduced in the previous sections, we need not apply domain knowledge to
simplify the analysis. Our tool identifies all leakage sites
reported by CacheD~\cite{203878} and find new leaks in less time.
We also find newer versions of RSA in OpenSSL have fewer leaks. Our tool can
finish all the analysis in less than 6 hours.

@@

The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. Under the circumstance, we think it is only a leakage.
We have confirmed that \tool{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \tool{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \tool{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours to process
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While those optimizations do not introduce false positives, they may miss some
vulnerabilities.
Third, CacheD only symbolizes the encryption keys. Some side-channel leakages when the input messages equal to some certain values. It is possible that CacheD miss some
leakages as we have discussion the previous sections.
We notice that the number of instructions in those traces are different due to the different analysis starting functions and building options during the evaluation.
Table~\ref{eval:cacheD} shows that
\tool{} is faster than CacheD. \tool{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\tool{} on AES from OpenSSL
0.9.7, \tool{} is over 100x faster than CacheD.
\begin{table*}[]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}

    \begin{tabular}{@{}l|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
      \hline
      \multicolumn{1}{l|}{} & \multicolumn{3}{c|}{CacheD} & \multicolumn{3}{c}{Abacus}                                             \\
      Name                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
      AES OpenSSL 0.9.7         & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
      AES OpenSSL 1.0.2f       & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
      RSA OpenSSL 0.9.7       & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
      RSA OpenSSL 1.0.2f     & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
      RSA Libgcrypt 1.6.1     & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
      RSA Libgcrypt 1.7.3         & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
      Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \tool: 12,489}                                 \\ \hline
    \end{tabular}

\end{table*}

DATA~\cite{217537} identifies
side-channel leakages by finding differences in execution traces of
the test program under \emph{various secret inputs}. According to
the original DATA paper, it uses 443 different traces to analyze the
side-channel vulnerabilities in symmetric cyphers and 450 different
traces to analyze the side-channel vulnerabilities in asymmetric
cyphers. On the other hand, \tool{} detects side-channel
vulnerabilities from one execution trace. \tool{} uses symbolic
analysis to extract formulas that model each side-channel
leakage. After that, we sample the formula with \emph{various
  secret inputs} to detect and quantify each leakage site. In
theory, DATA might have better code coverage than \tool{} because it
uses more execution traces,  but \tool{} has the following
advantages. a) \tool{} is faster than DATA. For example, it takes
116 minutes for DATA to detect vulnerabilities in the RSA implementation in OpenSSL 1.1.0f\@. \tool{} only spends 34 minutes, as shown in Table~\ref{table:over_result}. It takes 13 minutes and 20 minutes
for DATA to analyze the side-channel leakages in AES and DES,
respectively. On the other hand, \tool{} finishes its analysis in
less than ten seconds while finding all the leakages reported by
DATA. b) Because \tool{} does not run the test program again when wedinghao w
have a new \emph{secret input}, \tool{} can test more input secrets
on those formulas within the same time to achieve better precision.
c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
The strength of Abacus is that it does not need such domain knowledge.
DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
\tool{} finds the vulnerability.  For each leakage site, \tool{} can provide
concrete examples to trigger the issue and give an estimation to
assess the severity level of the vulnerability.

\section{Discussion}

\tool{} works on native x86 execution traces. The design, which is very
precise in terms of true leakages compared to other static source code
method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has
the common limitations of dynamic approaches. \tool{} may only cover part of the code.
Each time we only get one single execution trace. Therefore,
we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
However, this is not a crucial problem for analyzing crypto libraries because crypto
libraries are designed to have the same code coverage for various inputs. Our
evaluation also confirms the above point. For symmetric encryption, during our
evaluation there is no secret-dependent control-flow transfers. RSA
implementations have several secret-dependent control-flow transfers.
%But after we manually check those leakages cites. We find
Most of them are  %used for
bound checks, which do not leak much information and have negligible effects
on the whole code coverage as well.
